Through the eyes of the teacher

### 2021-02-08 paper_1/paper_1_supplement.Rmd
added coded speaking time

@@

# converting to integer to numeric
et.raw.data <- et.raw.data %>%  mutate(Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations))

@@

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Average Duration Fixation" = Average_duration_of_whole_fixations,
            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
view(et.raw.table)

@@

>>>>

quest.raw.data <- quest.raw.data %>% mutate (speaking.data)

@@

# converting integer to numeric
et.raw.data <- et.raw.data %>%  mutate(Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations))

@@

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Average Duration Fixation" = Average_duration_of_whole_fixations,
            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
            "TOI length" = TOI,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
view(et.raw.table)

@@

``` {r coded speaking time, echo = FALSE}
### read in data for 01_01_expert_D
speaking.data.01.01 <- read.table("./data/Aperol_pilot_01_01_expert_D_cam4.txt", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.01 <- speaking.data.01.01  %>% select(
  Dokumentgruppe,
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.01.01)

### checking for missing values
is.na(speaking.data.01.01)
which(is.na(speaking.data.01.01))

### filter only speaking time of teacher and "kodiert von Anna" as row 
speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
                                           Dokumentgruppe == "kodiert von Anna")

speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)

# read in data for 01_02_expert_A
speaking.data.01.02 <- read.table("./data/Aperol_pilot_01_02_expert_A_cam1_AL", dec=",", sep="\t", header=T)

### select relevant columns
speaking.data.01.02 <- speaking.data.01.02 %>% select(
  Dokumentgruppe,
  Dokumentname,
  Code,
  Anfang,
  Ende,
  Fläche,
  Abdeckungsgrad..)

str(speaking.data.01.02)

### checking for missing values
is.na(speaking.data.01.01)
which(is.na(speaking.data.01.01))

### filter only speaking time of teacher and "kodiert von Anna" as row 
speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
                                           Dokumentgruppe == "kodiert von Anna")

speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
